Sketch of DP - Bayesian Inference

### 2018-07-15 main-sketch.tex
abstract 3rd pass

\begin{abstract}
  Bayesian inference is a statistical method which allows to derive a
\emph{posterior} distribution over a parameter, starting from a
\emph{prior} distribution and observed data.  Many works have focused
on making this process differentially private adding noise on the
parameters representing the distributions\todo{cite?}.  Also, the
accuracy was measured using metrics on  the numeric
parameters representing the posterior distribution, e.g. $\ell_1$-norm
\todo{cite?}.

In this work we present a new mechanism for differentially private Bayesian
inference where the noise is added w.r.t  a smooth
sensitivity computed with a metric on probability distributions.
We also measure the accuracy of the process by using a metric over
probability measures.  We compared the accuracy of this approach with
the one based on the $\ell_1$-norm.  We present experimental results
showing that the former outperforms the latter.

>>>>

\begin{abstract}
Bayesian inference is a statistical method which allows to derive a
\emph{posterior} distribution over a parameter, starting from a
\emph{prior} distribution and observed data.  In a setting where the
data must be protected, different approaches have been taken to make
this process differentially
private. \citet{dimitrakakis2014robust}, and \citet{wang2015privacy}, for instance,
proved that, under specific conditions, sampling from the posterior distribution
is already differentially private.
Other works, e.g. \cite{zhang2016differential,foulds2016theory}, 
designed differentially private mechanisms that output a representation of the
full posterior distribution. Also,  accuracy of the mechanisms was measured
using metrics on the space of the numeric parameters of the posterior distribution,
e.g. $\ell_1$-norm .

In this work we present a new differentially private algorithm to compute the posterior.
The noise is calibrated w.r.t. a smooth sensitivity computed with
a metric on probability distributions; we measured the accuracy
of the process by using a metric over probability measures.
We compared the accuracy of this approach with the one
based on $\ell_1$-norm. Experimental results show that
when the data size is small or when the parameters of the prior
distribution are large, the former outperforms the latter.
